Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Secret-dependent Data Accesses}
Similar to secret-dependent control-flow transfers, a data access operation is
secret-dependent if different input sensitive keys ($K$) cause access to different memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits of the address are generally unimportant in side-channels.

>>>>

\subsection{Secret-dependent Data Accesses}
Similar to secret-dependent control-flow transfers, a data access operation is
secret-dependent if different input sensitive keys ($K$) cause accesses to different memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits of the address are generally unimportant in side-channels.
